### 2014-03-01 src/paper.Rnw
Adding operator fertility graph

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
@
<<chunk-hook, echo=2>>=
<<setup>>
@
\end{comment}

@@

% 10 pages for the main text + 1 for references.
\section{Introduction}
% 1. Describe the problem
% 2. State your contributions

@@

@@

<<>>=
s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
@

@@

We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
The number of mutators in RND is
 \Sexpr{sum(m$lrnd.pit.mutation.total) / sum(m$sdl.pit.mutation.total)} times SDL.

The total mutants for all is \Sexpr{sum(m$pit.mutation.total)}, for rnd is \Sexpr{sum(m$lrnd.pit.mutation.total)} and for sdl is \Sexpr{sum(m$sdl.pit.mutation.total)}

>>>>

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
@
<<chunk-hook, echo=2>>=
<<setup>>
@
\end{comment}

@@

% 10 pages for the main text + 1 for references.
\section{Introduction}
<<>>=
load('data/opdist.rda')
@
% 1. Describe the problem
% 2. State your contributions

@@

\subsection{Operators}

\subsection{Occurrence of Operators}
\begin{figure*}[t]
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.pit.all), stack(o.pit.all))
o.all$ind <- clean(o.all$ind)
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Original'))
o.det <- cbind(projects = rownames(o.pit.det), stack(o.pit.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))

r.all <- cbind(projects = rownames(r.pit.all), stack(r.pit.all))
r.all$ind <- clean(r.all$ind)
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Randoop'))
r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))
@
\caption{Relative fertility of mutation operators}
\label{fig:mfert}

\end{figure*}

@@

%<<>>=
%s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
%@

@@

We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
The number of mutators in RND is
 Sexpr{sum(m.lrnd.pit.mutation.total) / sum(m.sdl.pit.mutation.total)} times SDL.

The total mutants for all is Sexpr{sum(m.pit.mutation.total)}, for rnd is Sexpr{sum(m.lrnd.pit.mutation.total)} and for sdl is Sexpr{sum(m.sdl.pit.mutation.total)}
